### 2020-03-11 article_draft.tex
More edits

\documentclass{article}
\usepackage[margin = 0.5in]{geometry}
\usepackage[table]{xcolor}
\usepackage{amsmath,amsthm,amsfonts,dsfont,mathtools,float,setspace, booktabs, algorithm,tcolorbox,xparse,colortbl,longtable,array,multirow,wrapfig,float,pdflscape,tabu,threeparttable,threeparttablex,makecell,natbib}
\usepackage[normalem]{ulem}
\usepackage[english]{babel}
\bibliographystyle{plainnat}

\DeclarePairedDelimiter{\ceil}{\lceil}{\rceil}
\DeclarePairedDelimiter\floor{\lfloor}{\rfloor}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{refproof}{Proof}
\author{Adam Elder}
\newcommand{\bs}{\boldsymbol}
\newcommand{\sh}{\textcolor{red}}
\newcommand{\pr}{\text{Pr}}
\newcommand{\vmat}{\Sigma}
\newcommand{\indep}{\raisebox{0.05em}{\rotatebox[origin=c]{90}{$\models$}}}
\usepackage[mathscr]{euscript}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\definecolor{Gray}{gray}{0.95}
\newcommand{\rvo}{X}
\newcommand{\norm}{f}
\newcommand{\rvoo}{x}
\newcommand{\disto}{P}
\newcommand{\tst}{\hat{\boldsymbol{t}}}
\newcommand{\rvt}{Y}
\newcommand{\rvv}{Z}
\newcommand{\distv}{Q}
\newcommand{\pf}{\Phi}
\newcommand{\gi}{\Upsilon}

\begin{document} \section{Introduction}

\sh{In nearly all areas of high-dimensional statistics distinguishing between the important and unimportant predictors is of intrest}. In genetics many candidate snips and their association with some outcome is of interest. Many studies take measurements on a large number of biomarkers to predict medical outcomes such as the presence or progression of a disease. While there has been much focus on finding important predictors, there has been less interest in knowing if any predictors are actually important.  The vast number of potential predictors creates new statistical challenges to answering this less obvious question.

In the univariate case, once a measure of association is selected, standard approaches exist to construct asymptotically valid (and sometimes optimal) tests \citep{neyman_jerzy_ix._1933}. In this setting, a test is considered optimal if it achieves the largest power for every alternative compared to every other test with the same type one error.  However, scientists are often interested if any of a multitude of covariate are associated with the outcome of interest.  Even in the case with two covariates, a test with the above optimal property no longer exists and the alternative plays a larger role in which tests are more or less powerful.

To illustrate this, consider two tests with equal type one error rates. Both test the null that both of two association measures $\psi_1$, $\psi_2$ are zero. The first test focuses only on the $\psi_1$ and the second test considers both $\psi_1$ and $\psi_2$.  When the $\psi_1$ is non-zero $\psi_2$ is zero the first test can outperform all other tests.  Conversely when only $\psi_2$ is non-zero the first test will be outperformed by the second test.  Additionally in this setting, the power of these tests will be tied to the covariance between the covariates (a problem that did not exist for a single covariate).  These two factors make it difficult to define a test that performs well across all possible alternatives.  
% Even coming up with optimal properties for tests becomes difficult since it must make assumptions about the true data-generating mechanism.

Work with \textcolor{red}{simultaneous hypothesis testing}
%Tests capable of testing the union of multiple hypotheses simultaneously
began with Tukey in 1953 \citep{miller_simultaneous_1981}.  Previous work by Bonferroni was used by \citep{dunn_estimation_1959,dunn_multiple_1961} to come up with some of the first multiple hypothesis testing procedures.  Further improvements were proposed by \citep{hochberg_sharper_1988,holm_simple_1979,s._holland_improved_1988}.  Bonferroni-based correction procedures have the advantage of being easy to apply to already existing tests, while guaranteeing family-wise error control. However, these tests suffer from low power, especially in cases where the probability of rejecting each hypothesis is highly correlated.

@@

\begin{align*}
H_0: \psi_1 = \psi_2 = \dots = \psi_a = 0 \hspace{0.1cm}\text{  versus  } \hspace{0.1cm} H_1: \psi_j \neq 0 \text{ for some } j \in \{1, \dots, a\}.
\end{align*}
Last, let $\mathscr{M}$ denote the set of all possible distributions.  Define $\mathscr{M}_0 = \left\{ \disto \in \mathscr{M} : H_0 \text{ holds}  \right\}$

\subsection{Correlation Parameter}
We will compare our method to both a simple bonferroni correction method, and the method described in \citep{zhang_comment_2015}.  The settings considered will be the same as the firs setting in \citep{mckeague_adaptive_2015}.  The parameter of interest, $\psi_j(P)$ will be the correlation between the outcome of interest and the $j$'th covariate.

The vector of covariates in this setting will be generated from a normal distribution with mean zero and a variance covariance of $\Sigma$ with $\Sigma_{ij}$ equal to $\rho$ when $i \neq j$ and equal to 1 when $i = j$, and .  Three different models are considered.  Three different models for the outcome of interest ($Y$) will be considered. Letting $\varepsilon \sim N(0, 1)$ and be independent of $X$, the first model let $Y = \varepsilon$, the second has $Y = X_1 / 4$, and third has $Y = \sum_{k = 1}^{10} \beta_k X_k + \varepsilon$ where $\beta_k = 0.15$ for $k = \{1, \dots, 5\}$, and $\beta_k = -0.1$ for $k = \{6 \dots 10\}$.   in which Sample sizes of $100$ and $200$, dimensions of $10$, $50$, 100, 150, and 200, and $\rho$ of  $0, 0.5$, or $0.8$ will be considered,

\subsection{Missing Data Example}
In the second example, $Y$ is binary, $\Delta$ is a missingness indicator, and each $W_j$ is a covariate of interest.  When $\Delta = 0$ we don't observe $Y$.  The identifying assumption is $\Delta \indep Y | W$.  The parameter of interest is the risk ratio,
\begin{align*}
	\Psi_{j}\left(P^{\text{full}}\right) &= \frac{\text{Cov}\left(\log\left(Pr \left(Y = 1 |  W_j\right)\right), W_j\right)}{\text{Var}(W_j)}.\\
\end{align*}
Using the identifying assumption, the observed data parameter is:
\begin{align*}
	\tilde{\Psi}_{j}\left(P^{\text{obs}}\right)&= \frac{\text{Cov}\left(\log\left(E\left[Pr \left(\Delta  Y = 1 | \Delta = 1, W = W\right) |  W_j\right]\right), W_j\right)}{\text{Var}(W_j)}\\
\end{align*}

\textcolor{blue}{Right now, it seems that the time for a single test is quite a bit larger for this test than it is for the correlation test (which is reasonable), though it may speed up if Superlearner can be improved.  I am thinking of using similar simulation settings as was used before.}  There will be a single mechanism for the missingness, but it will be variable if the mechanism is known.  There will be three settings for between $W$ correlation.  All $W$ will be equally correlated, with $\rho = 0, 0.3$, or $0.7$.  Dimension will \textcolor{blue}{(depending on computation time)} be $10, 50, 100$ and possibly $200$.

There will be three settings for the $\beta$'s in the data generating model:
\begin{align*}
    \log(Pr(Y = 1 | W)) = \beta_0 + W^\top \beta
\end{align*}
In one setting $\beta = 0$.  In the second only one or two entries of $\beta$ will be non-zero.  In the last setting, many of the entries of $\beta$ will be non-zero (possibly $70$ or $80$ percent of the entries).

\subsection{Marginal Structural Model}
For this marginal structural model, we are interested in if the average treatment is modified by any covariates.  The marginal structural model for each $W_j$ is defined by
\begin{align*}
\text{logit}\left(Pr(Y^{(a)} = 1 | w)\right) = \beta_0 + \beta_1 a + \beta_2 w_j + \beta_3 w_j a
\end{align*}

\begin{align*}
(\beta_0^*, \beta_1^*, \beta_2^*, \beta_3^*) = \text{argmin}_{\beta_0, \beta_1, \beta_2, \beta_3}\int\left(\text{logit}\left(Pr(Y^{(a)} = 1 | w\right) - (\beta_0 + \beta_1 a + \beta_2w_j + \beta_3 w_j a) \right)^2 dP(w, a)
\end{align*}
The parameter of interest is $\beta_3^*$
\textcolor{blue}{The other $W_j$'s are included in the analysis and are marginalized over, but are not part of the defined model.} I am planning on using the same simulation settings as above, but also including non-changing effects for $a$, but am open to other ideas.
% \subsection{\sh{Something else possibly Tim's parameter (has something to do with survival)}}
% In this setting, the outcome is \sh{some measure of health}, and the covariates correspond to genetic measurements $W_{ij}$ that take value one for \sh{genes or snips which dont match the reference genome} and zero for those that do match. It is of interest if the measured outcome is associated with these genetic measurements.

@@

The test defined in \eqref{eqn:simp_test} is a function of three objects. The first was the chosen.  The second was $\sqrt{n}\hat{\boldsymbol{\psi}}$.  The third was the limiting distribution of $\sqrt{n}\hat{\boldsymbol{\psi}}$.  To simplify this test, replace  $\sqrt{n}\hat{\boldsymbol{\psi}}$ with $ \tst \equiv \sqrt{n}\Sigma^{-1/2}\hat{\boldsymbol{\psi}}$. Because $\tst$ will always converge to a standard multivariate normal regardless of which $P \in \mathscr{M}_0$ is true \textcolor{blue}{(point to proof)}, for the test defined using $\tst$:

\begin{align}
\label{eqn:simp_test_simp}
		\text{reject } H_0 \text{ if } \|\sqrt{n}\Sigma^{-1/2} \hat{\boldsymbol{\psi}}\|_2 \geq r_\alpha \text{ where } r_\alpha = \min\left\{r : Pr(\|\rvt\|_2 \leq r) \geq 1 - \alpha \right\} \text{ where } \rvt \sim N(\boldsymbol{0}, I).
\end{align}
has the property that $r_\alpha$ will not vary between null distributions. Using this simplification, the result of this test is determined by the norm chosen and the value of the test statistic.  Next consider this procedure in more generality. 
% \subsection{\textcolor{blue}{Creating a rejection region using a function}}
Consider a function $\Gamma$, of a vector in $\mathbb{R}^d$ (corresponding to $\tst$). While $\Gamma(x)$ should get larger as $x$ moves away from the null, $\Gamma$ can quite general.
%For the example of the $\ell_2$ norm, the p-value calculation was a function of the limiting distribution $Z$ and the test statistic $\sqrt{n}\hat{\boldsymbol{\psi}}$
% Because the limiting distribution of $\sqrt{n}\hat{\boldsymbol{\psi}}$ under $H_0$ is always a mean zero multivariate normal, we will index our general functions $\Gamma$ by the $d$ by $d$ variance covariance matrix instead of the infinite dimensional distribution function.
%   Under $H_0$, the limiting distribution of $\sqrt{n}\hat{\boldsymbol{\psi}}$ will be a mean zero multivariate normal distribution. 
An example of a more complicated $\Gamma$ is given below:
% any test defined using an acceptance region can also be carried out using a function, say $\Gamma_\distv(x)$ that maps from a value and distribution in $\mathbb{R}^d$.  Trivially, this function could be defined as: $\Gamma_{\distv(\disto)}(x) = I\{x \in \Theta_0(\disto)\}$.  However, in other cases, (for example the $\ell_2$ ball), this function can be more intuitive and can change depending on the norm.  
% In the previous example, $\Gamma_\distv(x) = Pr_\distv\left(\|\rvv\| \geq \|x\| \right)$.  For this definition of $\Gamma$, we knew the distribution of $\Gamma_\distv(\rvv)$ is uniformly distributed on $(0, 1)$.  However, for other $\Gamma$, this may not be the case. Consider 
\begin{align}
	\Gamma(x) &= Pr_\distv(\|\rvt + x\| > c_{0.8})  \text{ where }  c_{0.8} \equiv \min_{c}\{c : Pr(\|\rvt\| < c) \geq 0.8 \} \text{ and } \rvt \sim N(0, I). \label{gamma:pow}
\end{align}
Define the test using $\Gamma$ as 
\begin{align*}
	\text{reject } H_0 \text{ if } \Gamma(\tst) > c_{1 - \alpha} \text { where } c_{1 - \alpha} = \min_{c}\{c : \text{Pr}(\Gamma(Y) \geq c) < \alpha\} \text{ where } Y \sim N(\boldsymbol{0}, I)
\end{align*}
% \textcolor{blue}{I don't understand the end of this sentence}. 
% While the the above test has nice properties (type one error control, consistency), it is not clear how this test will perform compared to other tests with similar properties.

@@

To achieve this, first define $\Gamma_{1}(x), \dots, \Gamma_{p}(x)$ as collection of functions in which the functions only differ by the norm used in their definition. Next, define
% by defining a $\Gamma$ to those defined earlier, except the optimal norm is selected, and the corresponding summary value of $\Gamma$ with the optimal norm is returned.  For example, if we had $p$ different norms, $\norm_1, \dots, \norm_p$ and some summary function $\Gamma_\vmat(x, \|\cdot\|)$, we would define the adaptive version of $\Gamma$ as
\begin{align*}
	\Gamma^*(x) = \max\left\{\Gamma_{1}(x), \Gamma_{2}(x), \dots, \Gamma_{p}(x)\right\}.
\end{align*}
\textcolor{blue}{This could be the min if smaller values indicate larger distances away from the norm (such as p-values).}

While this function is more complicated than before,  $\Gamma^*(\rvt)$ can still be compared to $\Gamma^*(\tst)$ to obtain a p-value. Also, while it may be difficult to obtain the exact distribution of $\Gamma^*(\rvt)$, the distribution is a function of $\vmat$, so obtaining good approximations of $\Gamma^*(\rvt)$ is possible by taking many draws from $\rvt$.

@@

\begin{align*}
    \sqrt{n}\left(\hat{\boldsymbol{\psi}} - \boldsymbol{\psi}\right) \xrightarrow{d} \rvv \sim N\left(0, \Sigma\right)
\end{align*}
Under $H_0$, $\sqrt{n}\hat{\boldsymbol{\psi}}$ converges to $Z$, and $\Sigma$ can be approximated with $\widehat{\Sigma} = \frac{1}{n}\sum_{i = 1}^n D(\boldsymbol{x}_i) D(\boldsymbol{x}_i)^\top$.  In practice, a consistent estimator of $\vmat$, $\hat{\vmat}$ will be used in place of $\vmat$ for the calculation of $\tst$. Thus, the test statistic will be $\Gamma(\tst)$ will be compared to $\Gamma(\rvt)$.

\subsection{Using a permutation test for the test statistic}
While the above approach works asymptotically, there can be issues for small sample sizes.  To avoid inflated type one error, a permutation based test can be used.  Here, $\hat{\distv}^\#$ is used to define $\Gamma$, and the test will compare $\Gamma_{\hat{\distv}}(\sqrt{n} \hat{\boldsymbol{\psi}})$ to $\Gamma_{\hat{\distv}}(\rvv^\#)$. To determine $\hat{\distv}^\#$, the $Y$'s from the observed data are permuted before calculating $\widehat \Sigma$.  Draws from $\rvv^\#$ are taken by permuting all of the $Y$'s of the observed data.  \textcolor{blue}{There are a few more complications here that need to be figured out.}

@@

In the first set of experiments, we compare our method to both a Bonferroni based method and a tailor made method.  The Bonferroni based method computes a p-value for each covariate using a marginal linear regression.  If any p-value is smaller than the Bonferroni adjusted cutoff value, the null hypothesis is rejected. The method outlined by \citep{zhang_comment_2015} is similar to our method, but uses a parametric estimate of the correlation instead of using an influence function based estimator.  Four versions of our test are displayed in these plots. Our test that uses the $\ell_2$ norm, our test that uses the $\ell_\infty$ or max norm, and our test that selects over five possible $\ell_p$ norms.  The last version of our test selecs over many different versions of the following norm : $\|x\|_k = \sum_{i = 1}^k x_{(i)}^2$ where $x^2_{(i)}$ are the ordered statistics of $x^2$.

In each setting, each test is run 1000 times.  The proportion of tests that reject the null is plotted for each simulation setting and for each test.

@@

>>>>

\documentclass{article}
\usepackage[margin = 0.5in]{geometry}
\usepackage[table]{xcolor}
\usepackage{amsmath,amsthm,amsfonts,dsfont,mathtools,float,setspace, booktabs, algorithm,tcolorbox,xparse,colortbl,longtable,array,multirow,wrapfig,float,pdflscape,tabu, setspace, threeparttable,threeparttablex,makecell,natbib, pdfpages}
\usepackage[normalem]{ulem}
\usepackage[english]{babel}
\bibliographystyle{plainnat}

\DeclarePairedDelimiter{\ceil}{\lceil}{\rceil}
\DeclarePairedDelimiter\floor{\lfloor}{\rfloor}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{refproof}{Proof}
\author{Adam Elder}
\newcommand{\bs}{\boldsymbol}
\newcommand{\sh}{\textcolor{red}}
\newcommand{\pr}{\text{Pr}}
\newcommand{\vmat}{\Sigma}
\newcommand{\indep}{\raisebox{0.05em}{\rotatebox[origin=c]{90}{$\models$}}}
\usepackage[mathscr]{euscript}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\definecolor{Gray}{gray}{0.95}
\newcommand{\rvo}{X}
\newcommand{\norm}{f}
\newcommand{\rvoo}{x}
\newcommand{\disto}{P}
\newcommand{\tst}{\hat{\boldsymbol{t}}}
\newcommand{\rvt}{Y}
\newcommand{\rvv}{Z}
\newcommand{\distv}{Q}
\newcommand{\Gammaf}{\Gamma_{\Sigma}}
\newcommand{\Gammafe}{\Gamma_{\hat{\Sigma}}}
\newcommand{\pf}{\Phi}
\newcommand{\gi}{\Upsilon}

\begin{document} \section{Introduction}
\doublespacing

It is common across scientific disciplines to be interested in predicting an outcome using some (potentially large) number of covariates.  A first step to constructing accurate predictions is to find out if any covariate is associated with the outcome. Testing for the existence of an association can be done with a variety of existing methods, but frequently a trade off must be made between generalizability (ability to use the test for different parameters of interest and data generating mechanisms) and power (ability to detect an association when one exists).  We propose an approach testing for the existence of an association between an outcome and any number of covariates that can be carried out for most parameters of interest that performs nearly as well as tests designed for a specific parameter and data generating mechanism.  We compare our method with other modern methods in a simple simulated data setting.  We then study the tests performance in a setting with a complex sampling scheme, and a setting with a complex parameter of interest.

Back in the day, people used to think about which data to collect.  However, as it became cheaper, more and more data are collected without knowing if any of it can be predictive of the outcome of interest.  We gather many covariates rather than a single one, and whether any of them are predictive is an important first step to using them to do predictions.  It used to be assumed that the covariates we collected were in some way predictive of the outcome.  However, with data collection being so cheep, this is now a question that needs to be answered.

% Multiple hypotheses testing has been an area of interest since at least [].  However finding an elegant

% \sh{In nearly all areas of high-dimensional statistics distinguishing between the important and unimportant predictors is of intrest}. In genetics many candidate snips and their association with some outcome is of interest. Many studies take measurements on a large number of biomarkers to predict medical outcomes such as the presence or progression of a disease. While there has been much focus on finding important predictors, there has been less interest in knowing if any predictors are actually important.  The vast number of potential predictors creates new statistical challenges to answering this less obvious question.

% In the univariate case, once a measure of association is selected, standard approaches exist to construct asymptotically valid (and sometimes optimal) tests \citep{neyman_jerzy_ix._1933}. In this setting, a test is considered optimal if it achieves the largest power for every alternative compared to every other test with the same type one error.  However, scientists are often interested if any of a multitude of covariate are associated with the outcome of interest.  Even in the case with two covariates, a test with the above optimal property no longer exists and the alternative plays a larger role in which tests are more or less powerful.

% To illustrate this, consider two tests with equal type one error rates. Both test the null that both of two association measures $\psi_1$, $\psi_2$ are zero. The first test focuses only on the $\psi_1$ and the second test considers both $\psi_1$ and $\psi_2$.  When the $\psi_1$ is non-zero $\psi_2$ is zero the first test can outperform all other tests.  Conversely when only $\psi_2$ is non-zero the first test will be outperformed by the second test.  Additionally in this setting, the power of these tests will be tied to the covariance between the covariates (a problem that did not exist for a single covariate).  These two factors make it difficult to define a test that performs well across all possible alternatives.  
% Even coming up with optimal properties for tests becomes difficult since it must make assumptions about the true data-generating mechanism.

Work with \textcolor{red}{simultaneous hypothesis testing}
%Tests capable of testing the union of multiple hypotheses simultaneously
began with Tukey in 1953 \citep{miller_simultaneous_1981}.  Previous work by Bonferroni was used by \citep{dunn_estimation_1959,dunn_multiple_1961} to come up with some of the first multiple hypothesis testing procedures.  Further improvements were proposed by \citep{hochberg_sharper_1988,holm_simple_1979,s._holland_improved_1988}.  Bonferroni-based correction procedures have the advantage of being easy to apply to already existing tests, while guaranteeing family-wise error control. However because these tests ignore the joint distribution of the test statistics, they suffer from low power, especially in cases where the probability of rejecting each hypothesis is highly correlated.

@@

\begin{align*}
H_0: \psi_1 = \psi_2 = \dots = \psi_a = 0 \hspace{0.1cm}\text{  versus  } \hspace{0.1cm} H_1: \psi_j \neq 0 \text{ for some } j \in \{1, \dots, a\}.
\end{align*}

Last, let $\mathscr{M}$ denote the set of all possible distributions, and let $\mathscr{M}_0  \subset \mathscr{M}$ be the subset of distributions in $\mathscr{M}$ satisfying $H_0$.

We consider three different simulated data settings to study the test's performance.

\subsection{Correlation Parameter}
We will compare our method to a Bonferroni correct marginal testing method and the method described in \citep{zhang_comment_2015}.  The settings considered will be the same as the firs setting in \citep{mckeague_adaptive_2015}.  The parameter of interest, $\psi_j(P)$ will be the correlation between the outcome of interest and the $j$'th covariate.

The vector of covariates in this setting will be generated from a normal distribution with mean zero and a variance covariance of $\Sigma$ with $\Sigma_{ij}$ equal to $\rho$ when $i \neq j$ and equal to 1 when $i = j$. Three different models for the outcome of interest ($Y$) will be considered. For all considered settings, $\varepsilon \sim N(0, 1)$ and is independent of all $X$. In the first model $Y = \varepsilon$, in the second model $Y = X_1 / 4 + \varepsilon$, and in the third model $Y = \sum_{k = 1}^{10} \beta_k X_k + \varepsilon$ where $\beta_k = 0.15$ for $k = \{1, \dots, 5\}$, and $\beta_k = -0.1$ for $k = \{6 \dots 10\}$.  Sample sizes of $100$ and $200$, dimensions of $10$, $50$, $100$, $150$, and $200$, and $\rho$ of  $0, 0.5$, and $0.8$ are considered.  All combinations of model, sample size, dimension and $\rho$ are considered, and every test's performance is measured for all considered settings.

\subsection{Missing Data Example}
In the second example, $Y$ is binary, $\Delta$ is a missingness indicator, and each $W_j$ is a covariate of interest.  When $\Delta = 0$ we don't observe $Y$.  The identifying assumption is $\Delta \indep Y | W$, and the parameter of interest is the risk ratio under a poission working model for the probability that $Y = 1$.

\begin{align*}
	\Psi_{j}\left(P^{\text{full}}\right) &= \frac{\text{Cov}\left(\log\left(Pr \left(Y = 1 |  W_j\right)\right), W_j\right)}{\text{Var}(W_j)}.\\
\end{align*}

Using the identifying assumption, the observed data parameter is:

\begin{align*}
	\tilde{\Psi}_{j}\left(P^{\text{obs}}\right)&= \frac{\text{Cov}\left(\log\left(E\left[Pr \left(\Delta  Y = 1 | \Delta = 1, W = W\right) |  W_j\right]\right), W_j\right)}{\text{Var}(W_j)}\\
\end{align*}

The data are drawn from a binomial model:

\begin{align*}
    \log(Pr(Y = 1 | W)) = \beta_0 + W^\top \beta.
\end{align*}

There will be three settings considered which determine  the values of the $\beta$'s in the data generating model:

In all simulation settings the working model is used to take draws from $y$. In each setting, the vector $\boldsymbol{W}$ is draw from a multivariate normal with mean zero and covariance matrix $\Sigma_{DE2}$ where $\Sigma_{DE2, i, j} = 1$ for $i = j$ and $0.6$ for $i \neq j$.  $A$ is drawn from a binomial distribution independent from $W$.  For all three settings

\begin{align*}
	\text{logit}\left(Pr(Y = 1 | w, a)\right) = \sum_{i = 1}^{d} \beta_{i} w_i
\end{align*}

In the first setting $\beta_1 \dots \beta_d = 0$.  In the second setting $\beta_1 = 3$ and $\beta_2, \dots \beta_d = 0$.  In the last setting, $\beta_1 \dots \beta_5 = 1$, $\beta_6 \dots \beta_{10} = -1$ and $\beta_{11} \dots \beta_d = 0$.  Data are generated from all three models with every possible combination of sample size ($n = 100$, or $200$), and dimension ($d = 10, 50, 100, 150$, or $200$).

\subsection{Marginal Structural Model}
The third data example is a marginal structural model in which we test if the average treatment effect of a binary treatment $A$ is modified by any covariates $W_j$.  The marginal structural model for each $W_j$ is defined by the working model:

\begin{align*}
\text{logit}\left(Pr(Y^{(a)} = 1 | w)\right) = \beta_0 + \beta_1 a + \beta_2 w_j + \beta_3 w_j a
\end{align*}

in which our parameter of interest is:

\begin{align*}
(\beta_0^*, \beta_1^*, \beta_2^*, \beta_3^*) = \text{argmin}_{\beta_0, \beta_1, \beta_2, \beta_3}\int\left(\text{logit}\left(Pr(Y^{(a)} = 1 | w\right) - (\beta_0 + \beta_1 a + \beta_2w_j + \beta_3 w_j a) \right)^2 dP(w, a)
\end{align*}

The parameter of interest is $\beta_3^*$, but is worth noting that parameter is different from a usual logistic regression parameter because we are marginalizing over all $w_i$, not just $w_j$.

In all simulation settings the working model is used to take draws from $y$. In each setting, the vector $\boldsymbol{W}$ is draw from a multivariate normal with mean zero and covariance matrix $\Sigma_{DE3}$ where $\Sigma_{DE3, i, j} = 1$ for $i = j$ and $0.6$ for $i \neq j$.  $A$ is drawn from a binomial distribution independent from $W$.  For all three settings

\begin{align*}
	\text{logit}\left(Pr(Y = 1 | w, a)\right) = \beta_1 a + \sum_{i = 1}^{d} \beta_{i + 1} w_i + \sum_{j = 1}^d \gamma_{j} w_j a
\end{align*}

In every setting, $\beta_1 = 0.2$, $\beta_2, \dots \beta_{d/2 + 1} = 2/\sqrt{d}$, and $\beta_{d/2 + 1} \dots \beta_{d + 1} = 0$.  In the first (null) setting, $\gamma_{1} \dots \gamma{d} = 0$.  In the second setting, $\gamma_{1} = 3$ and $\gamma_{2} \dots \gamma_{d} = 0$.  In the final setting $\gamma_{1} \dots \beta_{5} = 1, \gamma_{6} \dots \beta_{10} = -1$, and $\gamma_{11} \dots \gamma_{d} = 0$.
Data are generated from all three models with every possible combination of sample size ($n = 100$, or $200$), and dimension ($d = 10, 50, 100, 150$, or $200$).

% \subsection{\sh{Something else possibly Tim's parameter (has something to do with survival)}}
% In this setting, the outcome is \sh{some measure of health}, and the covariates correspond to genetic measurements $W_{ij}$ that take value one for \sh{genes or snips which dont match the reference genome} and zero for those that do match. It is of interest if the measured outcome is associated with these genetic measurements.

@@

The test defined in \eqref{eqn:simp_test} is a function of three objects. The first was the chosen norm.  The second was $\sqrt{n}\hat{\boldsymbol{\psi}}$.  The third was the limiting distribution of $\hat{t} = \sqrt{n}\hat{\boldsymbol{\psi}}$.  Note that the limiting distribution of $\hat{t}$ under the null will always be a multivariate normal with mean zero with some covariance $\Sigma$. Thus potential tests can be defined using the finite dimensional $\Sigma$ matrix rather than the infinite dimension distribution $Q(P)$.  Choosing the $\ell_2$ norm, we can define our test by:

% To simplify this test, replace  $\sqrt{n}\hat{\boldsymbol{\psi}}$ with $ \tst \equiv \sqrt{n}\Sigma^{-1/2}\hat{\boldsymbol{\psi}}$. Because $\tst$ will always converge to a standard multivariate normal regardless of which $P \in \mathscr{M}_0$ is true \textcolor{blue}{(point to proof)}, for the test defined using $\tst$:

% \begin{align}
% \label{eqn:simp_test_simp}
% 		\text{reject } H_0 \text{ if } \|\sqrt{n} \hat{\boldsymbol{\psi}}\|_2 \geq r_\alpha \text{ where } r_\alpha = \min\left\{r : Pr(\|\rvt\|_2 \leq r) \geq 1 - \alpha \right\} \text{ where } \rvt \sim N(\boldsymbol{0}, \Sigma).
% \end{align}

% has the property that $r_\alpha$ will not vary between null distributions. Using this simplification, the result of this test is determined by the norm chosen and the value of the test statistic.

Next consider this procedure in more generality. 
% \subsection{\textcolor{blue}{Creating a rejection region using a function}}
Consider a function $\Gammaf$, of a vector in $\mathbb{R}^d$ (corresponding to $\tst$). While $\Gammaf(x)$ should get larger as $x$ moves away from the null, $\Gammaf$ can be quite general.
%For the example of the $\ell_2$ norm, the p-value calculation was a function of the limiting distribution $Z$ and the test statistic $\sqrt{n}\hat{\boldsymbol{\psi}}$
% Because the limiting distribution of $\sqrt{n}\hat{\boldsymbol{\psi}}$ under $H_0$ is always a mean zero multivariate normal, we will index our general functions $\Gamma$ by the $d$ by $d$ variance covariance matrix instead of the infinite dimensional distribution function.
%   Under $H_0$, the limiting distribution of $\sqrt{n}\hat{\boldsymbol{\psi}}$ will be a mean zero multivariate normal distribution. 
An example of a more complicated $\Gammaf$ is given below:
% any test defined using an acceptance region can also be carried out using a function, say $\Gamma_\distv(x)$ that maps from a value and distribution in $\mathbb{R}^d$.  Trivially, this function could be defined as: $\Gamma_{\distv(\disto)}(x) = I\{x \in \Theta_0(\disto)\}$.  However, in other cases, (for example the $\ell_2$ ball), this function can be more intuitive and can change depending on the norm.  
% In the previous example, $\Gamma_\distv(x) = Pr_\distv\left(\|\rvv\| \geq \|x\| \right)$.  For this definition of $\Gamma$, we knew the distribution of $\Gamma_\distv(\rvv)$ is uniformly distributed on $(0, 1)$.  However, for other $\Gamma$, this may not be the case. Consider 
\begin{align}
	\Gammaf(x) &= Pr_\distv(\|\rvt + x\| > c_{0.8})  \text{ where }  c_{0.8} \equiv \min_{c}\{c : Pr(\|\rvt\| < c) \geq 0.8 \} \text{ and } \rvt \sim N(0, \Sigma). \label{gamma:pow}
\end{align}
Define the test using $\Gammaf$ as 
\begin{align*}
	\text{reject } H_0 \text{ if } \Gammaf(\tst) > c_{1 - \alpha} \text { where } c_{1 - \alpha} = \min_{c}\{c : \text{Pr}(\Gammaf(Y) \geq c) < \alpha\} \text{ where } Y \sim N(\boldsymbol{0}, \Sigma)
\end{align*}
% \textcolor{blue}{I don't understand the end of this sentence}. 
% While the the above test has nice properties (type one error control, consistency), it is not clear how this test will perform compared to other tests with similar properties.

@@

To achieve this, first define $\Gamma_{\Sigma, 1}(x), \dots, \Gamma_{\Sigma, p}(x)$ as collection of functions in which the functions only differ by the norm used in their definition. Next, define
% by defining a $\Gamma$ to those defined earlier, except the optimal norm is selected, and the corresponding summary value of $\Gamma$ with the optimal norm is returned.  For example, if we had $p$ different norms, $\norm_1, \dots, \norm_p$ and some summary function $\Gamma_\vmat(x, \|\cdot\|)$, we would define the adaptive version of $\Gamma$ as
\begin{align*}
	\Gammaf^*(x) = \max\left\{\Gamma_{\Sigma, 1}(x), \Gamma_{\Sigma, 2}(x), \dots, \Gamma_{\Sigma, p}(x)\right\}.
\end{align*}
\textcolor{blue}{This could be the min if smaller values indicate larger distances away from the norm (such as p-values).}

While this function is more complicated than before,  $\Gammaf^*(\rvt)$ can still be compared to $\Gammaf^*(\tst)$ to obtain a p-value. Also, while it may be difficult to obtain the exact distribution of $\Gammaf^*(\rvt)$, the distribution is a function of $\vmat$, so obtaining good approximations of $\Gammaf^*(\rvt)$ is possible by taking many draws from $\rvt$.

@@

\begin{align*}
    \sqrt{n}\left(\hat{\boldsymbol{\psi}} - \boldsymbol{\psi}\right) \xrightarrow{d} \rvv \sim N\left(0, \Sigma\right)
\end{align*}
Under $H_0$, $\sqrt{n}\hat{\boldsymbol{\psi}}$ converges to $Z$, and $\Sigma$ can be approximated with $\widehat{\Sigma} = \frac{1}{n}\sum_{i = 1}^n D(\boldsymbol{x}_i) D(\boldsymbol{x}_i)^\top$.  In practice, a consistent estimator of $\vmat$, $\hat{\vmat}$ will be used in place of $\vmat$ for the calculation of $\tst$. Thus, the test statistic will be $\Gammaf(\tst)$ will be compared to $\Gammaf(\rvt)$.

\subsection{Using a permutation test for the test statistic}
While the above approach works asymptotically, there can be issues for small sample sizes.  To avoid inflated type one error, a permutation based test can be used.  Here, $\hat{\distv}^\#$ is used to define $\Gammaf$, and the test will compare $\Gamma_{\hat{\distv}}(\sqrt{n} \hat{\boldsymbol{\psi}})$ to $\Gamma_{\hat{\distv}}(\rvv^\#)$. To determine $\hat{\distv}^\#$, the $Y$'s from the observed data are permuted before calculating $\widehat \Sigma$.  Draws from $\rvv^\#$ are taken by permuting all of the $Y$'s of the observed data.  \textcolor{blue}{There are a few more complications here that need to be figured out.}

@@

% In the first set of experiments, we compare our method to both a Bonferroni based method and a tailor made method.  The Bonferroni based method computes a p-value for each covariate using a marginal linear regression.  If any p-value is smaller than the Bonferroni adjusted cutoff value, the null hypothesis is rejected. The method outlined by \citep{zhang_comment_2015} is similar to our method, but uses a parametric estimate of the correlation instead of using an influence function based estimator.  Four versions of our test are displayed in these plots. Our test that uses the $\ell_2$ norm, our test that uses the $\ell_\infty$ or max norm, and our test that selects over five possible $\ell_p$ norms.  The last version of our test selecs over many different versions of the following norm : $\|x\|_k = \sum_{i = 1}^k x_{(i)}^2$ where $x^2_{(i)}$ are the ordered statistics of $x^2$.

% In each setting, each test is run 1000 times.  The proportion of tests that reject the null is plotted for each simulation setting and for each test.

@@

\subsection*{Two Phase Sampling Risk Ratio}

\begin{figure}[]
	\centering
\includegraphics[width = \linewidth]{magnitude.pdf}
	\caption{Rejection rates across three different data generating mechanisms.}
	\label{fig:magnitude}
\end{figure}
